---
title: "Education Funding Inequality and Academic Performance Disparity between Migrant and Local Students in China"
shorttitle: "D2MR Final Project"
author:
  - name: Jiayi Zou
    corresponding: true
    email: jiayizou@uchicago.edu
    affiliations:
      - id: id1
        name: "University of Chicago"
        department: MA Program in the Social Sciences
        address: "1155 E 60th St."
        city: Chicago
        region: IL
        country: USA
        postal-code: 60637
author-note:
  disclosures:
    # Example: This article is based on the dissertation completed by [citation].  
    related-report: This project is the final assignment for Data to Manuscript in R (D2MR) instructed by Dr. Natalie Dowling. It also serves as an interim result of Jiayi Zou's MA thesis project. 
    # Example: The authors are grateful to [Person] for [Reason].
    gratitude: The author is grateful Dr. Dowling for supporting this project and offering guidance throughout the quarter.
abstract: "This document is a template demonstrating the apaquarto format. It includes examples of how to create figures and tables, as well as how to reference them in the text. The document is written in Quarto, a system for creating documents with R Markdown. The apaquarto extension provides a template for creating APA7-formatted manuscripts."
keywords: [education inequality, internal migration, education funding, fiscal decentralization]
floatsintext: true
numbered-lines: false
# File with references
bibliography: bibliography.bib
suppress-title-page: false
# Link citations to references
link-citations: true
draft-date: true
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  email: "Email"
  references-meta-analysis: "References marked with an asterisk indicate studies included in the meta-analysis."
format:
  apaquarto-html: default
  apaquarto-docx: default
  apaquarto-typst: 
    keep-typ: true
    list-of-figures: true
    list-of-tables: true
    toc: true
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: man
    keep-tex: true
    list-of-figures: true
    list-of-tables: true
    # Change default output size of figures unless specified in the chunk
    fig-width: 2
    fig-height: 2
    out-width: 40%
---

```{r}
#| label: setup
#| include: false

# Load necessary packages
library(tidyverse)
library(conflicted)
library(papaja)
library(flextable)
library(ftExtra)
library(knitr)
library(broom)
library(MASS) #robust regressions
library(knitr) #to use kable
library(estimatr) #to use lm_robust
library(sandwich) #to use lm.cluster


# use the conflicts_prefer function to avoid conflicts
conflicts_prefer(dplyr::filter, .quiet = TRUE)
conflicts_prefer(dplyr::select, .quiet =TRUE)
conflicts_prefer(flextable::separate_header, .quiet = TRUE)
conflicts_prefer(flextable::theme_apa, .quiet = TRUE) 

# Set seed
set.seed(1234)

# Generate r-references.bib file 
papaja::r_refs(file = "r-references.bib")

```

# Introduction
Internal migration in China has accelerated along with urbanization since the implementation of Reform and Opening Up policy in the early 1980s. Statistics from the 7th National Census in 2020 show that over 70 million children in China have migration status, which means one fourth of Chinese child population move interprovincially or intraprovincially with their parents ^[See in [Promoting reunion and avoiding separation - China's migrant children development report 2024](https://www.163.com/dy/article/JHFCU34705560ZWH.html).]. Education and sociology research focusing on internal migrant students found that these children have a relatively lower school achievement compared to local students without migrant status, and suffer from academic and financial difficulties, as well as alienation in public education system [@chenAccessPublicSchools2013; @huangMythMigrantsProblems2017a].

Previous studies offered policy explanations for migrant students’ underachievement. @liDataAnalysisCurrent2018 indicated that central governments have less educational funding distributed to provinces containing more migrant population due to fiscal decentralization. On the other hand, the *Hukou* policy ^[The *Hukou* Policy is a population management policy that restraints non-local residents from/uplifts the threshold of enjoying the same social, medical, and educational public services as local households do.] has a history of limiting policy supports for internal migrants including subsidies, fee standards, and other financial accesses, which contributes migrant students’ underperformance in school [@luVillagersCityResilience2023]. 

However, both perspectives have failed to identify an integrated framework: if we can discover the impact of differentiated financial supports and per student funding appropriated to two groups of students, then it is plausible to assume that fiscal decentralization is producing local-migrant educational inequity through the lens of *Hukou* status.

In this study, I seek to understand **how governments’ differentiated provision of education fundings affects the academic performance disparity between migrant students and local students in China** . My hypothesis is **when the government provides migrant students with limited fundings, and less-supportive charging standards and subsidy policies, the academic performance gap between the two groups of students is likely to widen**. 

Beyond measuring educational disparities created by the complexity of fiscal decentralization and population management system, this research has practical significance for addressing the ongoing migrant problems in China’s urban governance and the institution of compulsory education [@nationalbureauofstatisticsofchinaetal_2023_what]. Last but not least, this study can also offer indications for how educational finance and policies provided by government interacts with structural inequality in other social contexts (e.g., areas with higher poverty level or racial disparities, see in studies by @baird_2008_federal and @hyman_2017_does).

# Literature Review 

In this study, we define *provision of education fundings* as a combination of three elements: (1) the amount of funding, including per-student funding, subsidies, and charging standards; (2) the proportion of funding, which is seperated into central/provincial and county/district level; and (3) the indicator of differentiation, which is whether migrant students enjoy the equal educational financial resources as locally-registered students in terms of funding, subsidies, and charging standards. Inspired by @knoeppelEducationFundingStudent2015, we consider that education funding, influenced by fiscal decentralization and *Hukou* system, affects migrant and local students in the same schools through context for schooling, which results in unequal academic performances between two student groups.

## Education Funding and Academic Achievement

Scholarship in education funding suggests that students of color have been continuously underfunded by federal and state, and the discrepancy between their and higher-SES/white counterparts’ academic performance persists [@darling-hammond_2004_color; @gaddislauen_2014_school; @lafortuneetal_2018_school; @ryan_1999_schools]. In China, researchers found similar patterns and disparities among migrant students and local-*Hukou* students. Evidence from China Education Paney survey indicates that local students outperform migrant students at higher quantile point, and increasing total education expenditure is likely shrink the academic achievement gap [@fangStudyOutcomeEquity2024]. However, the association between other aspects of education expenditure (e.g. per student funding, central and local government appropriation ratio) and local-migrant academic outcome equity requires further exploration, as most studies center on how funding expands spatial education inequity rather than disparities between different *Hukou* statuses in cities [@weiAnalysisReportUrbanrural2022].

## Fiscal Decentralization and Descriminatory Policies against Internal Migrants

Beyond education finance disparities, education policies also differ for migrant and local students in many provinces, which means students without local registration (*hukou*) may have no government subsidies or face different charging standards. Researchers refer this phenomenon as deflecting internal migrants’ demands and using education to control urban population influx [@chanPhantomServicesDeflecting2019; @friedmanBiopoliticsUrbanizationChina2018]. The disadvantage encountered by migran students varies in different city scenarios: if local education policy background is more *Hukou*-based discriminatory, then migrant students are more likely to receive lower school performance than local students [@maMigrantStatusSchool2020]. Deflecting education resources away from the underprivileged students occurs in U.S. schools to avoid losing fundings under school accountability, as the minority subgroups have a higher possibility to fall short of the average academic target [@hanushekraymond_2005_does; @oday_2009_complexity]. Similarly, turning down education fundings for migrant students is also a strategy for Chinese local governments to decrease overall financial stress due to fiscal decentralization [@jinRegionalDecentralizationFiscal2005a; @longFiscalDecentralisationKnowledge2017].

As migrant students represent social minorities with limited or without *Hukou*-related rights in urban spaces, exploring their education achievements influenced by government funding and financial supports can demonstrate the dynamic and diverse efficiency of providing public services, offering empirical evidence for the development of decentralization theory [@oates_2008_evolution; @oatesSecondGenerationTheoryFiscal2005].

# Data and Methods

## Data 
In this project, we use the follow-up (2014-2015) dataset from the China Education Panel Survey [CEPS](http://ceps.ruc.edu.cn/English/Home.htm). CEPS is conducted by National Survey Research Center at Renmin University of China and it is the most used dataset in studies of Chinese internal migrant students. Data includes 1769 migrant students and 7960 non- migrant students who have valid information of migrant status in two phases of survey. We will merge datasets based on student, class, and school id, and remove values without valid information of hukou status.
```{r}
#| label: import-data
#| include: FALSE

library(haven) #to import STATA files

## import w2 data 
w2.st <- read_dta("./cepsw2data/cepsw2studentEN.dta")
w2.st.orig <- w2.st

## import w2 school data (principle data)
w2.pr <- read_dta("./cepsw2data/cepsw2principalEN.dta")
w2.pr.orig <- w2.pr

## import w2 parents data
w2.pa <- read_dta("./cepsw2data/cepsw2parentEN.dta")
w2.pa.orig <- w2.pa

# wrangling data
## merge w2 parent data with w2 student data
w2.st.pa <- w2.st.orig %>%
  left_join(w2.pa.orig, by = c("ids", "clsids", "w2clsids", "schids", "ctyids"))

## merge w2 school data with `w2.st.pa`
w2.join <- w2.pr.orig %>%
  left_join(w2.st.pa, by = c("schids", "ctyids"))

## select variables that account
w2.cleaned<- w2.join %>% 
  ## rename variables
  rename(## migrant status
         mig_status = w2a01, 
         ## school data
         per_st_funding = w2pla15, ## per student funding
         mig_funding = w2pla16, ## migrant student funding
         centgov_fund_pct= w2pla1701, ## central government funding percentage
         prefgov_fund_pct = w2pla1702, ## prefectural government funding percentage
         countgov_fund_pct = w2pla1703, ## county government funding percentage
         stucharge_pct = w2pla1704, ## student charging percentage
         same_charge_std = w2pld0200, ## same charging standard
         mig_subsidy = w2pld0405, ## whether migrant student are covered with subsidy
         ## parent data
         mig_locsch_access = w2bc07, ## can migrant students apply for local schools
         mig_locsch_require = w2bc0800, ## if so, what are the special requirements
         fam_fin = w2be23, ## family financial status-SES indicator
         fam_edu = w2be08, ## family education status-SES indicator
         fam_ocp = w2be09 ## family occupation status-SES indicator
  ) %>%
  mutate(
    # calculate the percentage of chinese, math, and english scores
    # in this way, when comparing the scores of migrant and non-migrant students, the outcome is standardized using percentage rather than raw score.
    w2chnstd = 100 * w2chn/w2upchn,
    w2matstd = 100 * w2mat/w2upmat,
    w2engstd = 100 * w2eng/w2upeng
  ) %>%
  ## select variables of interests
  select(
  ids, clsids, w2clsids, schids, ctyids, mig_status, w2chnstd, w2matstd, w2engstd, 
  per_st_funding, mig_funding, centgov_fund_pct, prefgov_fund_pct, countgov_fund_pct, stucharge_pct, 
  same_charge_std, mig_subsidy, mig_locsch_access, mig_locsch_require, fam_fin, fam_edu, fam_ocp
  ) 


# write out the dataframe
write_csv(w2.cleaned, "w2-cleaned.csv")

## investigate the structure of the data frame

str(w2.cleaned)

```

```{r}
#| label: data-cleaning

## in the `str()` function we have discovered certain issues with the dataframe that needs further improvements, 
## and we also want to drop NA values in `mig_status`

w2clean <- w2.cleaned %>%
  ## drop missing values in `mig_status`
  filter(!is.na(mig_status))  %>% 
  
  ## variables of migrant status, whether migrant students are provided with funding, 
  ## same charging standard, and subsidy, should all be vactors (without order)
  mutate(across(c(mig_status, mig_funding, same_charge_std, mig_subsidy), as.factor)) %>%
  
  ## deal with missing values 
  
  ## for continuous variables, subtitute the missing values with mean (compute mean for local and migrant students)
  group_by(mig_status) %>%  # group by mig_status
  # replace the missing exam score with the mean of each group 
  mutate(across(c(w2chnstd, w2matstd, w2engstd, 
                  per_st_funding, centgov_fund_pct, 
                  prefgov_fund_pct, countgov_fund_pct),
                ~ ifelse(is.na(.), mean(., na.rm = TRUE), .))) %>%
  # replace the missing per_st_funding, centgov_fund_pct, prefgov_fund_pct, countgov_fund_pct with the mean of each group 
  ungroup() %>%  # ungroup

  ## for categorical variables, subtitute the missing values with level "missing"
  mutate(across(c(mig_funding, same_charge_std, mig_subsidy), 
                ~ factor(replace_na(as.character(.), "missing"), levels = c(levels(.), "missing"))))

```


## Measures
The dependent variable in our study is the academic performance, which is measured by three indexes: score (percentage) of Chinese, Mathematics, and English exams. In [], a primary investigation into the follow-up dataset suggests that the medium and average of all three test scores for migrant students are all less than the equivalents for non-migrant students.
<!--  here's a figure (histogram) -->
As for the independent variable, we take three aspects into account: the amount of per-student funding and subsidies; the proportion of funding sources, which is seperated into central/provincial level and county/district level; and whether migrant students enjoy the equal funding, subsidies, and charging standards as locally-registered students do. 

## Methods


# Analysis Results


# Conclusion


\clearpage
# References
