---
title: "Education Funding Inequality and Academic Performance Disparity between Migrant and Local Students in China"
shorttitle: "D2MR Final Project"
author:
  - name: Jiayi Zou
    corresponding: true
    email: jiayizou@uchicago.edu
    affiliations:
      - id: id1
        name: "University of Chicago"
        department: MA Program in the Social Sciences
        address: "1155 E 60th St."
        city: Chicago
        region: IL
        country: USA
        postal-code: 60637
author-note:
  disclosures:
    # Example: This article is based on the dissertation completed by [citation].  
    related-report: This project is the final assignment for Data to Manuscript in R (D2MR) instructed by Dr. Natalie Dowling. It also serves as an interim result of Jiayi Zou's MA thesis project. 
    # Example: The authors are grateful to [Person] for [Reason].
    gratitude: The author is grateful Dr. Dowling for supporting this project and offering guidance throughout the quarter.
abstract: "Internal migration is an unique social problem for urban governance in China One of the major issue is the underperformance of migrant children in schools, and fiscal decentralization and the Hukou system restricts them from benefiting from the equal level of education finance as their local counterparts do. How governments’ differentiated provision of education fundings affects the academic performance disparity between migrant students and local students in China? Applying multilevel model, we found that after clustering two groups of students by school ids, migrant status can benefit migrant students' performance in Chinese exam, while their academic performance across three subjects can decrease due to excluding enrollment of migrants, lower quota of per-student funding, and missing information in subsidies and fiscal allocation."
keywords: [education inequality, internal migration, education funding, fiscal decentralization]
floatsintext: true
numbered-lines: false
# File with references
bibliography: bibliography.bib
suppress-title-page: false
# Link citations to references
link-citations: true
draft-date: true
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  email: "Email"
  references-meta-analysis: "References marked with an asterisk indicate studies included in the meta-analysis."
format:
  apaquarto-html: default
  apaquarto-docx: default
  apaquarto-typst: 
    keep-typ: true
    list-of-figures: true
    list-of-tables: true
    toc: true
  apaquarto-pdf:
    documentmode: man
    keep-tex: true
    list-of-figures: true
    list-of-tables: true
    fig-width: 2
    fig-height: 2
    tbl-width: 2
    tbl-height: 2
    out-width: 40%
---

```{r}
#| label: setup
#| include: false

# Load necessary packages
library(tidyverse)
library(conflicted)
library(papaja)
library(flextable)
library(ftExtra)
library(MASS) #robust regressions
library(knitr) #to use kable
library(estimatr) #to use lm_robust
library(sandwich) #to use lm.cluster


# use the conflicts_prefer function to avoid conflicts
conflicts_prefer(dplyr::filter, .quiet = TRUE)
conflicts_prefer(dplyr::select, .quiet =TRUE)
conflicts_prefer(flextable::separate_header, .quiet = TRUE)
conflicts_prefer(flextable::theme_apa, .quiet = TRUE) 
conflicts_prefer(lmerTest::lmer, .quiet = TRUE) # endure p-value can return in the MLM results

# Set seed
set.seed(1234)

# Generate r-references.bib file 
papaja::r_refs(file = "r-references.bib")

# Set knitr options, hide warnings and messages
knitr::opts_chunk$set(warning=FALSE, message=FALSE)

# source setting-up r.script
source("migrant-student-education-setting.R")
```

# Introduction
Internal migration in China has accelerated along with urbanization since the implementation of Reform and Opening Up policy in the early 1980s. Statistics from the 7th National Census in 2020 show that over 70 million children in China have migration status, which means one fourth of Chinese child population move interprovincially or intraprovincially with their parents ^[See in [Promoting reunion and avoiding separation - China's migrant children development report 2024](https://www.163.com/dy/article/JHFCU34705560ZWH.html).]. Education and sociology research focusing on internal migrant students found that these children have a relatively lower school achievement compared to local students without migrant status, and suffer from academic and financial difficulties, as well as alienation in public education system [@chenAccessPublicSchools2013; @huangMythMigrantsProblems2017a].

Previous studies offered policy explanations for migrant students’ underachievement. @liDataAnalysisCurrent2018 indicated that central governments have less educational funding distributed to provinces containing more migrant population due to fiscal decentralization. On the other hand, the *Hukou* policy ^[The *Hukou* Policy is a population management policy that restraints non-local residents from/uplifts the threshold of enjoying the same social, medical, and educational public services as local households do.] has a history of limiting policy supports for internal migrants including subsidies, fee standards, and other financial accesses, which contributes migrant students’ underperformance in school [@luVillagersCityResilience2023]. 

However, both perspectives have failed to identify an integrated framework: if we can discover the impact of differentiated financial supports and per student funding appropriated to two groups of students, then it is plausible to assume that fiscal decentralization is producing local-migrant educational inequity through the lens of *Hukou* status.

In this study, I seek to understand **how governments’ differentiated provision of education fundings affects the academic performance disparity between migrant students and local students in China** . My hypothesis is **when the government provides migrant students with limited fundings, and less-supportive charging standards and subsidy policies, the academic performance gap between the two groups of students is likely to widen**. 

Beyond measuring educational disparities created by the complexity of fiscal decentralization and population management system, this research has practical significance for addressing the ongoing migrant problems in China’s urban governance and the institution of compulsory education [@nationalbureauofstatisticsofchinaetal_2023_what]. Last but not least, this study can also offer indications for how educational finance and policies provided by government interacts with structural inequality in other social contexts (e.g., areas with higher poverty level or racial disparities, see in studies by @baird_2008_federal and @hyman_2017_does).

# Literature Review 

In this study, we define *provision of education fundings* as a combination of three elements: (1) the amount of funding, including per-student funding, subsidies, and charging standards; (2) the proportion of funding, which is seperated into central/provincial and county/district level; and (3) the indicator of differentiation, which is whether migrant students enjoy the equal educational financial resources as locally-registered students in terms of funding, subsidies, and charging standards. Inspired by @knoeppelEducationFundingStudent2015, we consider that education funding, influenced by fiscal decentralization and *Hukou* system, affects migrant and local students in the same schools through context for schooling, which results in unequal academic performances between two student groups.

## Education Funding and Academic Achievement

Scholarship in education funding suggests that students of color have been continuously underfunded by federal and state, and the discrepancy between their and higher-SES/white counterparts’ academic performance persists [@darling-hammond_2004_color; @gaddislauen_2014_school; @lafortuneetal_2018_school; @ryan_1999_schools]. In China, researchers found similar patterns and disparities among migrant students and local-*Hukou* students. Evidence from China Education Paney survey indicates that local students outperform migrant students at higher quantile point, and increasing total education expenditure is likely shrink the academic achievement gap [@fangStudyOutcomeEquity2024]. However, the association between other aspects of education expenditure (e.g. per student funding, central and local government appropriation ratio) and local-migrant academic outcome equity requires further exploration, as most studies center on how funding expands spatial education inequity rather than disparities between different *Hukou* statuses in cities [@weiAnalysisReportUrbanrural2022].

## Fiscal Decentralization and Descriminatory Policies against Internal Migrants

Beyond education finance disparities, education policies also differ for migrant and local students in many provinces, which means students without local registration (*hukou*) may have no government subsidies or face different charging standards. Researchers refer this phenomenon as deflecting internal migrants’ demands and using education to control urban population influx [@chanPhantomServicesDeflecting2019; @friedmanBiopoliticsUrbanizationChina2018]. The disadvantage encountered by migran students varies in different city scenarios: if local education policy background is more *Hukou*-based discriminatory, then migrant students are more likely to receive lower school performance than local students [@maMigrantStatusSchool2020]. Deflecting education resources away from the underprivileged students occurs in U.S. schools to avoid losing fundings under school accountability, as the minority subgroups have a higher possibility to fall short of the average academic target [@hanushekraymond_2005_does; @oday_2009_complexity]. Similarly, turning down education fundings for migrant students is also a strategy for Chinese local governments to decrease overall financial stress due to fiscal decentralization [@jinRegionalDecentralizationFiscal2005a; @longFiscalDecentralisationKnowledge2017].

As migrant students represent social minorities with limited or without *Hukou*-related rights in urban spaces, exploring their education achievements influenced by government funding and financial supports can demonstrate the dynamic and diverse efficiency of providing public services, offering empirical evidence for the development of decentralization theory [@oates_2008_evolution; @oatesSecondGenerationTheoryFiscal2005].

# Data and Methods
```{r}
#| label: import-data
#| include: FALSE

library(haven) #to import STATA files

## import w2 data 
w2.st <- read_dta("./cepsw2data/cepsw2studentEN.dta")
w2.st.orig <- w2.st

## import w2 school data (principle data)
w2.pr <- read_dta("./cepsw2data/cepsw2principalEN.dta")
w2.pr.orig <- w2.pr

## import w2 parents data
w2.pa <- read_dta("./cepsw2data/cepsw2parentEN.dta")
w2.pa.orig <- w2.pa

# wrangling data
## merge w2 parent data with w2 student data
w2.st.pa <- w2.st.orig %>%
  left_join(w2.pa.orig, by = c("ids", "clsids", "w2clsids", "schids", "ctyids"))

## merge w2 school data with `w2.st.pa`
w2.join <- w2.pr.orig %>%
  left_join(w2.st.pa, by = c("schids", "ctyids"))

## select variables that account
w2.cleaned<- w2.join %>% 
  ## rename variables
  rename(## migrant status
         mig_status = w2a01, 
         ## school data
         per_st_funding = w2pla15, ## per student funding
         mig_funding = w2pla16, ## migrant student funding
         centgov_fund_pct= w2pla1701, ## central government funding percentage
         prefgov_fund_pct = w2pla1702, ## prefectural government funding percentage
         countgov_fund_pct = w2pla1703, ## county government funding percentage
         stucharge_pct = w2pla1704, ## student charging percentage
         same_charge_std = w2pld0200, ## same charging standard
         mig_subsidy = w2pld0405, ## whether migrant student are covered with subsidy
         ## parent data
         mig_locsch_access = w2bc07, ## can migrant students apply for local schools
         mig_locsch_require = w2bc0800, ## if so, what are the special requirements
         fam_fin = w2be23, ## family financial status-SES indicator
         fam_edu = w2be08, ## family education status-SES indicator
         fam_ocp = w2be09 ## family occupation status-SES indicator
  ) %>%
  mutate(
    # calculate the percentage of chinese, math, and english scores
    # in this way, when comparing the scores of migrant and non-migrant students, the outcome is standardized using percentage rather than raw score.
    w2chnstd = 100 * w2chn/w2upchn,
    w2matstd = 100 * w2mat/w2upmat,
    w2engstd = 100 * w2eng/w2upeng
  ) %>%
  ## select variables of interests
  select(
  ids, clsids, w2clsids, schids, ctyids, mig_status, w2chnstd, w2matstd, w2engstd, 
  per_st_funding, mig_funding, centgov_fund_pct, prefgov_fund_pct, countgov_fund_pct, stucharge_pct, 
  same_charge_std, mig_subsidy, mig_locsch_access, mig_locsch_require, fam_fin, fam_edu, fam_ocp
  ) 

## investigate the structure of the data frame

str(w2.cleaned)

```

```{r}
#| label: data-cleaning

## in the `str()` function we have discovered certain issues with the dataframe that needs further improvements, 
## and we also want to drop NA values in `mig_status`

w2clean <- w2.cleaned %>%
  ## drop missing values in `mig_status`
  filter(!is.na(mig_status))  %>% 
  
  ## variables of migrant status, whether migrant students are provided with funding, 
  ## same charging standard, and subsidy, should all be vactors (without order)
  mutate(across(c(mig_status, mig_funding, same_charge_std, mig_subsidy), as.factor)) %>%
  
  ## deal with missing values 
  
  ## for continuous variables, subtitute the missing values with mean (compute mean for local and migrant students)
  group_by(mig_status) %>%  # group by mig_status
  # replace the missing exam score with the mean of each group 
  mutate(across(c(w2chnstd, w2matstd, w2engstd, 
                  per_st_funding, centgov_fund_pct, 
                  prefgov_fund_pct, countgov_fund_pct),
                ~ ifelse(is.na(.), mean(., na.rm = TRUE), .))) %>%
  # replace the missing per_st_funding, centgov_fund_pct, prefgov_fund_pct, countgov_fund_pct with the mean of each group 
  ungroup() %>%  # ungroup

  ## for categorical variables, subtitute the missing values with level "missing"
  mutate(across(c(mig_funding, same_charge_std, mig_subsidy), 
                ~ factor(replace_na(as.character(.), "missing"), levels = c(levels(.), "missing"))))

# write out the dataframe
write_csv(w2clean, "w2-cleaned.csv")


```
## Data 
In this project, we use the follow-up (2014-2015) dataset from the China Education Panel Survey [CEPS](http://ceps.ruc.edu.cn/English/Home.htm). CEPS is conducted by National Survey Research Center at Renmin University of China and it is the most used dataset in studies of Chinese internal migrant students. Data includes `r sum(w2clean$mig_status==2)` migrant students and `r sum(w2clean$mig_status==1)` non-migrant students who have were at 9th Grade as in the final year of Junior High. We will merge datasets based on student, class, and school id, and remove values without valid information of hukou status.

## Measures
The dependent variable in our study is the academic performance, which is measured by three indexes: score (percentage) of Chinese, Mathematics, and English exams. In @fig-box-academic-performance, a primary investigation into the follow-up dataset suggests that the medium and average of all three test scores for migrant students are all less than the equivalents for non-migrant students. Migrant students performances in Chinese and English exams are more concentrated than local students, but possibly due to different sample size. More outliers in Chinese exam scores appeared in migrant student group than their local counterparts, suggesting migrant students might experience greater difficulty in achieveing in Chinese exams.
Additionally, the average Chinese, Mathematics and English exam scores of migrant students are respectively `r mean(w2clean$w2chnstd[w2clean$mig_status==2])`, `r mean(w2clean$w2matstd[w2clean$mig_status==2])`, and `r mean(w2clean$w2engstd[w2clean$mig_status==2])`, which are lower than their local counterparts' academic achievements (`r mean(w2clean$w2chnstd[w2clean$mig_status==1])`, `r mean(w2clean$w2matstd[w2clean$mig_status==1])`, and `r mean(w2clean$w2engstd[w2clean$mig_status==1])`).
<!--here's a boxplot  -->
```{r}
#| label: fig-box-academic-performance
#| fig-cap: "Comparison of the distribution of Chinese, Mathematics, and English exam scores (Migrant vs. Local students)"
#| fig-width: 5
#| fig-height: 4


## Organize the dataframe in to a form better for ggplot function to generate plots
df_long <- w2clean %>%
  select(mig_status, w2chnstd, w2matstd, w2engstd) %>%
  # concert exams scores into a long column named "subject" and "score"
  pivot_longer(cols = c(w2chnstd, w2matstd, w2engstd), 
               names_to = "subject", values_to = "score") %>%
  mutate(subject = recode(subject, 
                          "w2chnstd" = "Chinese", 
                          "w2matstd" = "Math", 
                          "w2engstd" = "English")) %>%
  # scores more than 100 are defined as outliers
  filter(score <= 100)

## draw boxplot
ggplot(df_long, aes(x = subject, y = score, fill = factor(mig_status))) +
  geom_boxplot() + 
  # regulate the scale of y-axis 
  scale_y_continuous(breaks = seq(0, 100, by = 10)) +
  # use the palette we defined in rscript
  scale_fill_manual(values = palette_apa, labels = c("Local", "Migrant")) +
  labs(x = "Subject", y = "Score", fill = "Student Type") +
  # use the theme_apa function
  theme_minimal() +
  theme_apa()

```

As for the independent variable, we take three aspects into account: the amount of per-student funding; the proportion of funding sources, which is seperated into central/provincial level and county/district level; and whether migrant students enjoy the equal funding, subsidies, and charging standards as locally-registered students do. 
<!-- here's a t-test table  -->
```{r}
#| label: tbl-ttest-two-sample-perfunding
#| tbl-caption: "Two-sample t-test on the mean per-student funding across program types"
#| tbl-pos: H

library(kableExtra)

# Two-sample t-test of per-student funding by migrant status
ttest2_per <- t.test(
       filter(w2clean, mig_status == "1")$per_st_funding, # local students
       filter(w2clean, mig_status == "2")$per_st_funding # migrant students
       )

# summarize the model
ttest2_per_df <- data.frame(
  `Statistic (t)` = ttest2_per$statistic,
  `df` = ttest2_per$parameter,
  `P-value` = round(ttest2_per$p.value, 3),
  `Mean (Local students)` = ttest2_per$estimate[1],
  `Mean (Migrant students)` = ttest2_per$estimate[2],
  check.names = FALSE
)

kable(ttest2_per_df,
          format = "latex", booktabs = TRUE) %>%
          kable_styling(latex_options = "scale_down")

```
In @tbl-ttest-two-sample-perfunding, we examined the difference of mean per-student funding for local and migrant students. The results indicate that the average per-student funding is significantly different in two student subgroups, with a $p$-value of `r round(ttest2_per$p.value, 3)`. It is worth noticing that the mean funding for each migrant student (`r ttest2_per$estimate[2]`) is higher than the local student's (`r ttest2_per$estimate[1]`), which aligns with the policy guidance from central government in China. The result is also counterintuitive with the reverse comparison of academic achievements in @fig-box-academic-performance. These findings call for further investigation in the the effect of educational funding provision on academic achievement inequality.

## Methods

We employ a **Multilevel Model (MLM)** to see the effect of independent variables on the academic performance gap between migrant students and local students. Since migrant students and local students are clustered in different schools, MLM can provide a hierarchical model fitness that can take cluster effect into account [@antonoplisStudyingSocioeconomicStatus2023].
We will implement random intercept, fixed slope model to examine the research question primarily. When analyzing data in later procedures, MLM can be adjusted with improvement in significance tests and improvement in fit. The two-level model can be put in an incorporated formula:
<!-- Forgive me for writing the function so ugly. It's so long and the only way latex won't return error when rendering pdf is to keep it this way -->
$$ examscore_{ij}= \beta_0 + \beta_1 \cdot mig\_status + \beta_2 \cdot centgov\_fund\_pct_j + \beta_3 \cdot prefgov\_fund\_pct_j $$
$$+\beta_4 \cdot countgov\_fund\_pct_j + \beta_5 \cdot per\_st\_funding_j + \beta_6 \cdot mig\_funding_j + \beta_7 \cdot same\_charge\_std_j$$
$$ + \beta_8 \cdot mig\_subsidy_j  + \beta_9 \cdot (mig\_status_{ij} \times centgov\_fund\_pct_j) $$
$$ + \beta_{10} \cdot (mig\_status_{ij} \times prefgov\_fund\_pct_j) + \beta_{11} \cdot (mig\_status_{ij} \times countgov\_fund\_pct_j) $$
$$ + \beta_{12} \cdot (mig\_status_{ij} \times per\_st\_funding_j)  + \beta_{13} \cdot (mig\_status_{ij} \times mig\_funding_j) $$
$$ + \beta_{14} \cdot (mig\_status_{ij} \times same\_charge\_std_j)  + \beta_{15} \cdot (mig\_status_{ij} \times mig\_subsidy_j) + u_j + \epsilon_{ij} $$
<!-- End of the ugly formula -->
In this funtion, we denote *i* as the individual student and *j* as the school. The estimate for the fixed effect are as follows: (1) $\beta_0$ is the overall intercept; (2) $\beta_1$ stands for the effect of being a migrant student; (3) $\beta_2$ to $\beta_8$ extimate the effects of independent variables; (4) $\beta_9$ to $\beta_15$ extimate the interaction effects of independent variables and migrant status; (5) $u_j$ is the random intercept for school *j*; and (6) $\epsilon_{ij}$ represents the residual error.

# Analysis Results

## Linear Relation between Per-student Funding and Academic Achievements 

We first investigated the correlation between per-student funding and exam scores. @fig-ggplot-funding-score shows that the linear relation between per-student funding and academic achievements is positive across student groups and subjects. The estimate for the relation of Chinese exam score with per-student funding is relatively smaller than the other two subjects. However, we cannot observe a significant difference in this relation between local student and migrant student groups.

```{r}
#| label: fig-ggplot-funding-score
#| fig-cap: "The linear relation between per-student funding and exam scores across two student groups"
#| fig-width: 6
#| fig-height: 5

# convert the dataframe into longer version
w2clean_long <- w2clean %>%
  pivot_longer(
    cols = c(w2chnstd, w2matstd, w2engstd),  
    names_to = "subject",  # store subject of the score
    values_to = "score"  # store exam score
  )

# compute geom_smooth with two facets
ggplot(w2clean_long, aes(x = per_st_funding, y = score, color = factor(mig_status))) +
 
  # plotting points with transparency
  geom_point(alpha = 0.5, size = 0.5 ) +  
  
  # adding black smooth line and "se" to show confidence intervals
  # hide the formula so it won't appear in PDF
  geom_smooth(method = "lm", se = TRUE, color = "black", linewidth = 0.5) +  
  
  # seperate the plot in two facets (by subject of exam and migrant status)
  facet_wrap(~ subject + mig_status, labeller = labeller(mig_status = c("1" = "Local Students", "2" = "Migrant Students"), subject = c("w2chnstd" = "Chinese", "w2matstd" = "Math", "w2engstd" = "English"))) +  
  labs(
    x = "Per-Student Funding",
    y = "Exam Score",
    color = "Migrant Status"  # set legend titles
  ) +
  
  scale_color_manual(
    values = palette_apa,  # set colors
    labels = c("1" = "Local Students", "2" = "Migrant Students")  # set legend labels
  ) +
  
  theme_minimal() +
  theme(
    legend.position = "bottom",  # setting the position of the legend
    axis.text.x = element_text(angle = 45, hjust = 1)  # rotate the x axises
  )
```
## The Effect of Education Funding on Academic Achievments in Different Student Groups

In this section, we employed the MLM method to estimate the effect of educational funding on the exam scores in three subjects. In the results, the estimate of the migrant status variable `mig_status` represents $\beta_1$, which is the effect of being a migrant student on the overall academic performance. The rest of the estimates are for the independent variables or interaction terms.

```{r}
#| label: tbl-chinese-achievement
#| tbl-cap: "The effect of education funding on Chinese exam scores differences within schools"
#| warning: FALSE

# for formatted tables that can dit multilevel model
if (!require(broom.mixed)) {
 install.packages("broom.mixed")  
 library(broom.mixed)  
}

# install.packages("lmerTest")
library(lmerTest) # to conduct multilevel model (with p.value)

# fit the multilevel model for Chinese scores
model_chi <- lmer(w2chnstd ~ mig_status + per_st_funding + centgov_fund_pct + prefgov_fund_pct + countgov_fund_pct + mig_funding + same_charge_std + mig_subsidy + mig_status:per_st_funding + mig_status:centgov_fund_pct + mig_status:prefgov_fund_pct + mig_status:countgov_fund_pct + mig_status:mig_funding + mig_status:same_charge_std + mig_status:mig_subsidy + (1 | schids), data = w2clean)

# extract the results
report_lmer(model_chi)
  
```
@tbl-chinese-achievement computes the regression outcome of the funding effect on Chinese exam scores, with cluster effect of schools. The estimate for migrant status is `r round(fixef(model_chi)["mig_status2"], 3)`, indicating a significant postive impact on the academic performance in Chinese exam with a $p$-value of `r round(summary(model_chi)$coefficients["mig_status2", "Pr(>|t|)"], 3)`. This finding refutes our previous hypothesis that being a migrant student can negatively influence one's academic performance. Within the same school, migrant students averagely outperform local students in Chinese exam by `r round(fixef(model_chi)["mig_status2"], 3)` with significance.
The results in the table also suggest that one-unit higher per-student funding can increase the individual's Chinese exam score by `r round(fixef(model_chi)["per_st_funding"], 3)`. The rest of the independent variables including proportion of funding resources and whether migrant students enjoy the equal level of educational finance resources has no significant impact on the academic performance in Chinese exam. However, when the school does not enroll migrant students, and the context of whether migrant students and local students share the same charging standard and subsidies is missing, migrant students tend to suffer from a significant negative impact and a lower Chinese exam score than local students.


```{r}
#| label: tbl-math-achievement
#| tbl-cap: "The effect of education funding on Mathematics exam scores differences within schools"
#| warning: FALSE

# fit the multilevel model for Chinese scores
model_mat <- lmer(w2matstd ~ mig_status + per_st_funding + centgov_fund_pct + prefgov_fund_pct + countgov_fund_pct + mig_funding + same_charge_std + mig_subsidy + mig_status:per_st_funding + mig_status:centgov_fund_pct + mig_status:prefgov_fund_pct + mig_status:countgov_fund_pct + mig_status:mig_funding + mig_status:same_charge_std + mig_status:mig_subsidy + (1 | schids), data = w2clean)

# extract the results
report_lmer(model_mat)
```

@tbl-math-achievement computes the regression outcome of the funding effect on Math exam scores, with cluster effect of schools. The estimate for migrant status is not significant, but still has a postive impact on the academic performance in Math exam with a $p$-value of `r round(summary(model_mat)$coefficients["mig_status2", "Pr(>|t|)"], 3)`. One-unit higher per-student funding can increase the individual's Math exam score by `r round(fixef(model_mat)["per_st_funding"], 3)`, with a significance of `r round(summary(model_mat)$coefficients["per_st_funding", "Pr(>|t|)"], 3)`. 
We can also see that the an increase in the proportion of education fiscal appropriation from Prefecture level has a significant negative impact on individual's Math exam score. Similar with what we found in the funding effect on Chinese exam performance, the rest of the independent variables has no significant impact on the academic performance in Math exam. And when the school does not enroll migrant students, and the context of whether migrant students and local students share the same charging standard and subsidies is missing, migrant students tend to suffer from a significant negative impact and a lower Math exam score than local students.
It is significant that when the quota of fiscal allocation for migrant students is less than that of the local students, the Math exam score of migrant students will drastically decrease by `r round(fixef(model_mat)["mig_status2:mig_funding2"], 3)`, with a $p$-value of `r round(summary(model_mat)$coefficients["mig_status2:mig_funding2", "Pr(>|t|)"], 3)`.

```{r}
#| label: tbl-english-achievement
#| tbl-cap: "The effect of education funding on English exam scores differences within schools"
#| warning: FALSE

# fit the multilevel model for Chinese scores
model_eng <- lmer(w2engstd ~ mig_status + per_st_funding + centgov_fund_pct + prefgov_fund_pct + countgov_fund_pct + mig_funding + same_charge_std + mig_subsidy + mig_status:per_st_funding + mig_status:centgov_fund_pct + mig_status:prefgov_fund_pct + mig_status:countgov_fund_pct + mig_status:mig_funding + mig_status:same_charge_std + mig_status:mig_subsidy + (1 | schids), data = w2clean)

# extract the results
report_lmer(model_eng)
```

Lastly, @tbl-english-achievement computes the regression outcome of the funding effect on English exam scores, with cluster effect of schools. The estimate for migrant status is not significant. And the finding of per-student funding effect on individual's English exam score is identical with our previous discoveries in @tbl-chinese-achievement and @tbl-math-achievement. Most independent variables has no significant impact on the academic performance in English exam. When the information of whether migrant students enjoy the equal level of subsidies with local students is missing, individual student may increase their English exam score by a `r round(fixef(model_eng)["mig_subsidymissing"], 3)`, with a significance of `r round(summary(model_eng)$coefficients["mig_subsidymissing", "Pr(>|t|)"], 3)`
And when the school does not enroll migrant students, and the information of whether migrant students and local students share the same subsidies is missing, migrant students tend to suffer from a significant negative impact and a lower English exam score than local students (with corresponding estimates of `r round(fixef(model_eng)["mig_status2:mig_funding4"], 3)` and `r round(fixef(model_eng)["mig_status2:mig_subsidymissing"], 3)`.

# Conclusion
This study examines the impact of differentiated educational funding on the academic performance disparity between migrant and local students in China, within the broader social context of fiscal decentralization and the Hukou system. Using a multilevel modeling approach that accounts for school-level clustering, our findings challenge the conventional assumption that migrant status inherently disadvantages students academically. In the Chinese exam, migrant students demonstrate a significant performance advantage over their local counterparts within the same school. However, across all three subjects (Chinese, Math, and English), educational funding allocation plays a crucial role in shaping academic outcomes.

Specifically, higher per-student funding is consistently associated with improved exam scores, while discrepancies in fiscal allocation, particularly when migrant students receive lower quotas or when key financial information is missing, contribute to their academic disadvantage. The exclusion of migrant students from certain schools further exacerbates disparities, leading to significant negative impacts on their performance. Additionally, a higher proportion of educational funding from the prefecture level is found to negatively affect math achievement, suggesting potential inefficiencies in decentralized funding structures.

These findings highlight the urgent need for policy interventions aimed at ensuring equitable access to educational resources for migrant students. Policymakers should prioritize increasing transparency in fiscal allocations, equalizing per-student funding across student groups, and addressing institutional barriers that restrict migrant students' school enrollment. Addressing these systemic inequalities is essential for fostering a more inclusive and equitable urban education system in China.

\clearpage
# References
